---
title: "Exploring Neural Activity in Steinmetz Mouse Experiment"
author: "Seok Hyun Kim"
date: "2023-06-10"
output: html_document
---

STA 141 Project 

Abstract:
-------------------------------------------

Our project is based on the Steinmetz mouse experiment conducted in 2019. The study aimed to examine the behavior of 10 male and female mice by analyzing the activities of approximately 30,000 neurons across 42 brain areas. The researchers discovered that prior to starting a task, the brain's overall activity could predict how engaged the mice would be during each trial and throughout the entire task. When the mice were engaged, their lower-level brain activity (subcortical) became stronger, while their higher-level brain activity (neocortical) became weaker.

In our project, we focused on a subset of data from the Steinmetz experiment, specifically data from four out of the ten mice. We examined the spiking activity of neurons in various crucial brain areas between trials and within sessions, identifying trends in response time and engagement variability. Through this analysis, we observed that the mice named Cori and Lederberg exhibited similar patterns of neuron activity, while Hench and Forssmann showed similar trends in neuron activity. Furthermore, we discovered that neuron spiking activity in the root area and the CA area played a significant role in understanding the mice's neuron activity.

Using this information, we made predictions about the actions of Hench and Lederberg during their sessions in the Steinmetz experiment.
Section 1 Introduction:
-------------------------------------------
# Introduce the objective and briefly review the background of this data set 

The four different mice chosen from the Steinmetz mouse experiment to be included in our data analysis were: Cori, Forssman, Hench, and Lederberg. Cori participated in sessions 1-3, Forssman in sessions 4-7, Hench in sessions 8-12, and Lederberg in sessions 13-18. Each session consisted of approximately 100-500 trials. During each trial, the mouse was exposed to visual stimuli displayed on a screen. These visual stimuli varied in intensity, with values of 0, 0.25, 0.5, and 1 on both the left and right sides. The stimuli intensity of both sides is recorded as variables left_contr. and right_contr.

If the left stimuli had a stronger intensity, the mouse's successful task was to turn the wheel to the left. Conversely, if the right stimuli were stronger, the successful task was to turn the wheel to the right. When both left and right stimuli had equal intensities, the correct wheel turning direction was randomized. In each trial, the mouse received a reward for successfully completing the task and a penalty for failure. The correctness of the mouse for each trial is recorded as the variable "feedback," -1 for incorrect and 1 for correct.

Throughout the experiment, scientists monitored the neural activities of each mouse, specifically focusing on the spikes of stimulation occurring in their neurons. The scientists recorded the spiking trains of each responsive neuron 0.4 seconds after the onset of stimulation. Additionally, they noted the location of each neuron in the brain.

The purpose of this project is to predict the feedback type of 100 random trials each from session 1 and session 18 using the mice's neuron activity and data trends.

First, we load the packages that we need to run the code in our project, as well as the data from our experiment.
```{r}
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages("devtools")
knitr::opts_chunk$set(eval = TRUE, echo = TRUE, fig.align='center')
install.packages("tidyverse")
library(tidyverse)
install.packages("knitr")
library(knitr)
install.packages("dplyr")
library(dplyr)
install.packages("kableExtra")
install.packages("rvest")
library(kableExtra)
library(rvest)
```

```{r}
session=list()
for(i in 1:18){
  session[[i]]=readRDS(paste('~/Downloads/sessions/session',i,'.rds',sep=''))
}
```


Section 2 Exploratory analysis:
-------------------------------------------
#i.describe the data structures across sessions (e.g., number of neurons, number of trials, stimuli conditions, feedback types)

First, we create a data frame with variables summarizing key aspects of this experiment, with each row representing one of the 18 sessions. Each session includes the following information: mouse_name (the name of the mouse), date_exp (the date the session occurred), n_brain_area (the number of brain areas with active neurons in that session), n_neurons (the number of active neurons in that session), n_trials (the number of trials in that session), and the success rate. The success rate is calculated by taking the feedback types (1 for correct actions of mice in a trial, -1 for incorrect actions of mice in a trial) and determining the rate of correct actions, which directly summarizes our response variable.
```{r}
n.session=length(session)

meta <- tibble(
  mouse_name = rep('name',n.session),
  date_exp =rep('dt',n.session),
  n_brain_area = rep(0,n.session),
  n_neurons = rep(0,n.session),
  n_trials = rep(0,n.session),
  success_rate = rep(0,n.session)
)

for(i in 1:n.session){
  tmp = session[[i]];
  meta[i,1]=tmp$mouse_name;
  meta[i,2]=tmp$date_exp;
  meta[i,3]=length(unique(tmp$brain_area));
  meta[i,4]=dim(tmp$spks[[1]])[1];
  meta[i,5]=length(tmp$feedback_type);
  meta[i,6]=mean(tmp$feedback_type+1)/2;
  }
```

```{r}
# In package knitr-just formatting meta
kable(meta, format = "html", table.attr = "class='table table-striped'",digits=2) 
```
One variable that I feel may have a relationship with our response variable (feedback types/success rate) is n_neurons.

I found the average of n_neurons for each mouse as well as their average success rate.
```{r}
#average number of active neurons for each mouse

# Create separate data frames for each mouse's sessions
cori_sessions <- session[sapply(session, function(x) x$mouse_name == "Cori")]
forssmann_sessions <- session[sapply(session, function(x) x$mouse_name == "Forssmann")]
hench_sessions <- session[sapply(session, function(x) x$mouse_name == "Hench")]
lederberg_sessions <- session[sapply(session, function(x) x$mouse_name == "Lederberg")]

# Calculate the average number of neurons for each mouse's sessions
cori_avg_neurons <- mean(sapply(cori_sessions, function(x) dim(x$spks[[1]])[1]))
forssman_avg_neurons <- mean(sapply(forssmann_sessions, function(x) dim(x$spks[[1]])[1]))
hench_avg_neurons <- mean(sapply(hench_sessions, function(x) dim(x$spks[[1]])[1]))
lederberg_avg_neurons <- mean(sapply(lederberg_sessions, function(x) dim(x$spks[[1]])[1]))

# Print the average number of neurons for each mouse's sessions
cat("Cori's average number of neurons:", cori_avg_neurons, "\n")
cat("Forssman's average number of neurons:", forssman_avg_neurons, "\n")
cat("Hench's average number of neurons:", hench_avg_neurons, "\n")
cat("Lederberg's average number of neurons:", lederberg_avg_neurons, "\n")

```
```{r}
#average success rate for each mouse

# Create separate data frames for each mouse's sessions
cori_sessions <- session[sapply(session, function(x) x$mouse_name == "Cori")]
forssman_sessions <- session[sapply(session, function(x) x$mouse_name == "Forssmann")]
hench_sessions <- session[sapply(session, function(x) x$mouse_name == "Hench")]
lederberg_sessions <- session[sapply(session, function(x) x$mouse_name == "Lederberg")]

# Calculate the average success rate for each mouse's sessions
cori_avg_success <- mean(sapply(cori_sessions, function(x) mean(x$feedback_type + 1) / 2))
forssman_avg_success <- mean(sapply(forssman_sessions, function(x) mean(x$feedback_type + 1) / 2))
hench_avg_success <- mean(sapply(hench_sessions, function(x) mean(x$feedback_type + 1) / 2))
lederberg_avg_success <- mean(sapply(lederberg_sessions, function(x) mean(x$feedback_type + 1) / 2))

# Print the average success rate for each mouse's sessions
cat("Cori's average success rate:", cori_avg_success, "\n")
cat("Forssman's average success rate:", forssman_avg_success, "\n")
cat("Hench's average success rate:", hench_avg_success, "\n")
cat("Lederberg's average success rate:", lederberg_avg_success, "\n")

```
I plotted the two averages of the 4 mice into a plot to see if there is a relationship between the average number of active neurons and average success rate.
```{r}
library(ggplot2)

# Calculate average success rate and average number of neurons for each mouse
mouse_names <- c("Cori", "Forssman", "Hench", "Lederberg")
avg_success <- c(cori_avg_success, forssman_avg_success, hench_avg_success, lederberg_avg_success)
avg_neurons <- c(cori_avg_neurons, forssman_avg_neurons, hench_avg_neurons, lederberg_avg_neurons)

# Create a data frame with the mouse names, average success rate, and average number of neurons
data <- data.frame(Mouse = mouse_names, Avg_Success = avg_success, Avg_Neurons = avg_neurons)

# Create the dot plot
dot_plot <- ggplot(data, aes(x = Avg_Success, y = Avg_Neurons, color = Mouse)) +
  geom_point(size = 3) +
  labs(x = "Average Success Rate", y = "Average Number of Neurons") +
  scale_color_manual(values = c("Cori" = "blue", "Forssman" = "green", "Hench" = "red", "Lederberg" = "purple"))

# Display the dot plot
print(dot_plot)

```
We cannot see a clear relationship between the average n_neurons or average success rate between the 4 mice. We will investigate the variability and trends of neuron spiking activity further, as well as a better method to predict the feedback types throughout this project.

#ii.explore the neural activities during each trial

Below is the code that summarizes the neuron spiking activity from each trial by calculating the average number of spikes across neurons in the same brain area. We have encapsulated this code within a function that takes the session and trial numbers as input, allowing us to apply the code easily to different sessions and trials throughout the experiment. We have tested this code on session 2, trial 1, which is also performed by Cori, the subject of the test data from session 1.
```{r}
i.s=2 # indicator for this session

i.t=1 # indicator for this trial 

spk.trial = session[[i.s]]$spks[[i.t]]
area=session[[i.s]]$brain_area

# We need to first calculate the number of spikes for each neuron during this trial 
spk.count=apply(spk.trial,1,sum)

# for(i in 1:dim(spk.trial)[1]){
#  spk.count[i]=sum(spk.trial[i,])
# }

# Next we take the average of spikes across neurons that live in the same area 

# You can use tapply() or group_by() in dplyr

# tapply():
spk.average.tapply=tapply(spk.count, area, mean)


# dplyr: 
# To use dplyr you need to create a data frame
tmp <- data.frame(
  area = area,
  spikes = spk.count
)
# Calculate the average by group using dplyr
spk.average.dplyr =tmp %>%
  group_by(area) %>%
  summarize(mean= mean(spikes))
```

```{r}
# Wrapping up the function:

average_spike_area<-function(i.t,this_session){
  spk.trial = this_session$spks[[i.t]]
  area= this_session$brain_area
  spk.count=apply(spk.trial,1,sum)
  spk.average.tapply=tapply(spk.count, area, mean)
  return(spk.average.tapply)
  }

# Test the function
average_spike_area(1,this_session = session[[i.s]])
```
Now we can see the average spike counts for the areas of the brain that had active spiking neurons in session 2 trial 1 (CA1, POST, root, VIS1, VISpm).

Moving on, we make another data frame called trial.summary that summarizes the neuron activity from all the trials in a session, also including other characteristics of the experiment that may be helpful information for the response variable of our prediction model (feedback type) such as the left stimuli value, right stimuli value, and trial id. Each experiment includes the average spike counts for all brain area where there was active neuron spiking activity.

We obtain the trial summary of session 2.
```{r}
n.trial=length(session[[i.s]]$feedback_type)
n.area=length(unique(session[[i.s]]$brain_area ))
# Alternatively, you can extract these information in the meta that we created before.

# We will create a data frame that contain the average spike counts for each area, feedback type,  the two contrasts, and the trial id

trial.summary =matrix(nrow=n.trial,ncol= n.area+1+2+1)
for(i.t in 1:n.trial){
  trial.summary[i.t,]=c(average_spike_area(i.t,this_session = session[[i.s]]),
                          session[[i.s]]$feedback_type[i.t],
                        session[[i.s]]$contrast_left[i.t],
                        session[[i.s]]$contrast_right[i.s],
                        i.t)
}

colnames(trial.summary)=c(names(average_spike_area(i.t,this_session = session[[i.s]])), 'feedback', 'left contr.','right contr.','id' )

# Turning it into a data frame
trial.summary <- as_tibble(trial.summary)
head(trial.summary, 15)
```
Roughly observing the first 15 trials of session 2, we can see that the higher average spike counts in the root area seem to have negative feedback types. For instance, trial 1 (feedback -1) has an average spike count of 1.5384615 in the root area while trial 2 (feedback 1) has a much lower average spike count of 0.9358974. We can also observe a similar trend for the CA1 area. Trial 1 (feedback -1) has an average spike count of 1.816753 in the root area while trial 2 (feedback 1) has a much lower average spike count of 1.0366492.	

According to my sources, the CA1 area of the brain is connected to the retrieval of episodic memory, while the root area is connected to the control of the sleep/wake cycle. One possible explanation for these neuron spiking trends are that in many trials that Cori was losing engagement, Cori was daydreaming (therefore more spikes in CA1) and/or his brain was sending signals for him to wake up (therefore more spikes in root). 

Then we create a visualization plotting the neuron spiking activities for the each area of the brain 0.4 seconds post onset. Each dot represents a neuron spike, and each area of the brain is color coded in a different color.
We take a look at the neuron spiking activity in session 2 trial 1.
```{r}
area.col <- c("red","orange","green","blue", "purple")

plot.trial<-function(i.t,area, area.col,this_session){
    
    spks=this_session$spks[[i.t]];
    n.neuron=dim(spks)[1]
    time.points=this_session$time[[i.t]]
    
    plot(0,0,xlim=c(min(time.points),max(time.points)),ylim=c(0,n.neuron+1),col='white', xlab='Time (s)',yaxt='n', ylab='Neuron', main=paste('Trial ',i.t, 'feedback', this_session$feedback_type[i.t] ),cex.lab=1.5)
    for(i in 1:n.neuron){
        i.a=which(area== this_session$brain_area[i]);
        col.this=area.col[i.a]
        
        ids.spike=which(spks[i,]>0) # find out when there are spikes 
        if( length(ids.spike)>0 ){
            points(x=time.points[ids.spike],y=rep(i, length(ids.spike) ),pch='.',cex=5, col=col.this)
        }
      
            
    }
    
legend("topright", 
  legend = area, 
  col = area.col, 
  pch = 16, 
  cex = 0.8
  )
  }
varname=names(trial.summary);
area=varname[1:(length(varname)-4)]
plot.trial(1,area, area.col,session[[i.s]])
```
We can see that the neuron spikes are the most dense around 88.6-88.7 seconds for all brain areas, but especially in the VISpm area. This indicates that it takes around 0.2 seconds before the neurons in Cori's brain react to the stimuli.

#iii.explore the changes across trials
Now we form a plot that enables us to oversee the average spike counts for each active area of the brain across all trials in a session, so that we can observe trends on how the spike counts differ as the trials proceed. 
We create a plot for session 2 once again.
```{r}
area.col=rainbow(n=n.area,alpha=0.7)
# In base R, I usually initiate a blank plot before drawing anything on it
plot(x=1,y=0, col='white',xlim=c(0,n.trial),ylim=c(0.5,2.2), xlab="Trials",ylab="Average spike counts", main=paste("Spikes per area in Session", i.s))


for(i in 1:n.area){
  lines(y=trial.summary[[i]],x=trial.summary$id,col=area.col[i],lty=2,lwd=1)
  lines(smooth.spline(trial.summary$id, trial.summary[[i]]),col=area.col[i],lwd=3)
  }
legend("topright", 
  legend = colnames(trial.summary)[1:n.area], 
  col = area.col, 
  lty = 1, 
  cex = 0.8
)
```
We can see that the spike counts in the CA1 area take a dip around trials 50-150. This indicates that the neurons in the CA1 area in Cori's brain(the subject of this session) tend to become less active in the middle of the session, possibly out of temporarily losing engagement in the task.
We can also see a similar trend for the spike counts in the root area around trials 40-175, although less drastic.
The spike counts in the VIS1 area and VISpm area seem relatively constant with no drastic declines or increases in their spike counts, which could indicate that Cori's visual cortex tends to stay around the same level of activeness throughout the session.

#iv.explore homogeneity and heterogeneity across sessions and mice.
We will now be investigating whether these neuron trends are homogeneous/heterogenous across sessions that Cori participated in. This is important in building our prediction model because our test data comes from session 1 experimented on Cori, and session 18 experimented on Lederberg. We would like to know if all sessions conducted by Cori and Lederberg will show similar neuron activity.

We plot the above visualization for all 3 sessions that Cori was the subject of (session 1-3) to see whether his neuron spiking activity across trials differ between sessions.

In order to create a function that can generate the plot for different session numbers, we encapsulate the code responsible for producing the plot within a function. Similarly, we create another function to generate the trial summary by encapsulating the corresponding code.
```{r}
#trial summary function
process_session <- function(session_num) {
  n.trial <- length(session[[session_num]]$feedback_type)
  n.area <- length(unique(session[[session_num]]$brain_area))
  
  trial.summary <- matrix(nrow = n.trial, ncol = n.area + 1 + 2 + 1)
  
  for (i.t in 1:n.trial) {
    trial.summary[i.t,] <- c(average_spike_area(i.t, this_session = session[[session_num]]),
                            session[[session_num]]$feedback_type[i.t],
                            session[[session_num]]$contrast_left[i.t],
                            session[[session_num]]$contrast_right[i.t],
                            i.t)
  }
  
  colnames(trial.summary) <- c(names(average_spike_area(i.t, this_session = session[[session_num]])),
                               'feedback', 'left contr.', 'right contr.', 'id')
  
  trial.summary <- as_tibble(trial.summary)
  
  return(trial.summary)
}

#plot function
plot_spike_counts <- function(session_number) {
  i.s <- session_number
  trial.summary <- process_session(session_number)
  n.trial <- max(trial.summary$id)
  n.area <- ncol(trial.summary) - 4
  min.spike <- min(unlist(trial.summary[, -c(1:4)]))
  max.spike <- max(unlist(trial.summary[, -c(1:4)]))
  
  area.col <- rainbow(n = n.area, alpha = 0.7)
  
  plot(x = 1, y = 0, col = 'white', xlim = c(0, n.trial), ylim = c(0.5, 3), 
       xlab = "Trials", ylab = "Average spike counts", 
       main = paste("Spikes per area in Session", i.s))
  
  for (i in 1:n.area) {
    lines(y = trial.summary[[i]], x = trial.summary$id, col = area.col[i], lty = 2, lwd = 1)
    lines(smooth.spline(trial.summary$id, trial.summary[[i]]), col = area.col[i], lwd = 3)
  }
  
  legend("topright", 
         legend = colnames(trial.summary)[1:n.area], 
         col = area.col, 
         lty = 1, 
         cex = 0.8
  )
}

```

```{r}
#session 1
plot_spike_counts(1)
#session 2
plot_spike_counts(2)
#session 3
plot_spike_counts(3)
```
We can see through these 3 plots that Cory has much higher spike counts for multiple brain areas in the first and last session (session 1 and 3), and much lower spike counts in the middle session (session 2). This could indicate that Cori drastically lost engagement in the middle of the experiment,hence the neurons in many areas of his brain were not responsive to the stimuli.

We will now be investigating whether these neuron activity trends are homogeneous/heterogenous across mice. This is important because we would like to know the differences in neuron activity between the two mice in our test data set (Cori and Lederberg) as well as whether the other two mice subjects (Forssman and Hence) show similarity in neuron activity to Cori or Lederberg. 
In our approach we are choosing one representative session from each mouse (session 1 for Cori, session 18 for Lederberg, session 6 for Forssmann, session 10 for Hench), and examining the neuron spiking activity in first and last trials of their representative sessions. In doing this, we can see how each mouse's neuron spiking activity changes at the start and end of their trials.
```{r}
#Cori's beginning and end trial
trial.summary<-process_session(1)
varname=names(trial.summary);
area=varname[1:(length(varname)-4)]
par(mfrow=c(1,2))
plot.trial(1,area, area.col,session[[1]])
plot.trial(114,area, area.col,session[[1]])
```
```{r}
#Lederberg's beginning and end trial
trial.summary<-process_session(18)
varname=names(trial.summary);
area=varname[1:(length(varname)-4)]
par(mfrow=c(1,2))
plot.trial(1,area, area.col,session[[18]])
plot.trial(108,area, area.col,session[[18]])
```
```{r}
#Forssman's beginning and end trial
trial.summary<-process_session(6)
varname=names(trial.summary);
area=varname[1:(length(varname)-4)]
par(mfrow=c(1,2))
plot.trial(1,area, area.col,session[[6]])
plot.trial(290,area, area.col,session[[6]])
```

```{r}
#Hench's beginning and end trial
trial.summary<-process_session(10)
varname=names(trial.summary);
area=varname[1:(length(varname)-4)]
par(mfrow=c(1,2))
plot.trial(1,area, area.col,session[[10]])
plot.trial(447,area, area.col,session[[10]])
```
We can see that for both Cori and Lederberg, the neuron spiking activity in the beginning trial (trial 1 for both mice) has a denser distribution of neuron spikes in the second half of their 0.4 seconds onset. However, the neuron spiking activity in the ending trial (trial 114 for Cori, trial 108 for Lederberg) has a denser distribution of neuron spikes in the first half of their 0.4 seconds onset. This trend is especially prevalent in their brain areas CA3 and root. 

On the other hand, for both Hench and Forssman, the neuron spiking activity in both the beginning and end trials have a denser distribution of neuron spikes in the first half of their 0.4 seconds onset.

This indicates that for Cori and Lederberg, the neurons in their brain take a longer time to react to stimuli in the beginning of their session but are trained to react faster by the end of the session. On the other hand, for Hench and Forssman, the neurons in their brain take a short time to react to stimuli from the beginning.

We conclude that Cori and Lederberg (the two mice in our test data) show similarities in neuron spiking activity. While Hench and Forssman share similarities in neuron spiking activity with each other, their data trends are noticeably different from Cori and Lederberg.

Section 3 Data integration
---------------------------------------

#i.extracting the shared patterns across sessions

After observing distinct differences in the neuron spiking activities of Hench and Forssman compared to Cori and Lederberg, we make the decision to focus solely on the sessions involving Cori and Lederberg for a more accurate prediction model. We extract the trial summaries from the sessions conducted with Cori and Lederberg and combine them into a single data frame named combined_df. This consolidation allows us to streamline the data for further analysis and prediction modeling.  
```{r}
#extract trial summary for all 18 sessions first 

for (i in 1:18) 
{

  # Assign the trial summary to a unique data frame name
  assign(paste0("session", i), process_session(i))
}

#Combine Cori and Lederberg's sessions into one data frame
df_cori <- bind_rows(session1, session2, session3)
head(df_cori)
df_lederberg <- bind_rows(session13, session14, session15, session16, session17, session18)
head(df_lederberg)
library(plyr)
combined_df <- rbind.fill(df_cori, df_lederberg)
head(combined_df)
```

#ii.addressing the differences between sessions.
Now we determine which brain area had the most frequent spiking activity through all the trials in combined_df by seeing the brain areas with the least number of "NA"s in their average spike count value. We assume that the neuron spiking activity in these brain areas will be the most accurate in helping us predict the feedback type in each trial.
```{r}
na_counts <- colSums(is.na(combined_df))
na_counts_df <- data.frame(variable = names(na_counts), na_counts = na_counts)
na_counts_df <- na_counts_df[order(na_counts_df$na_counts), ]
head(na_counts_df )
combined_df[is.na(combined_df)] <- 0
```

We find that the top 4 brain areas with the most frequent neuron spiking activity are root, LGd, CA1 and CA3. Earlier in our "exploring homogenity/heterogenity in sessions and mice" section we found the neuron spiking trends in the neuron spiking activity of root and CA3 to be representative of Cori and Lederberg's neuron activity within a session. Therefore, we decide use the average spike counts of neurons in root, CA3, LGd, and CA1 to be the main predictor variables in our prediction model. 


Section 4 Predictive modeling
--------------------------------------
Since our experimental data is complex, consisting of over 1000 trials across 18 sessions, it is reasonable to assume that there may be a few outlier trials where Cori and Lederberg were distracted or an incident occurred that affected their performance accuracy. To address this, we have chosen to employ LDA on our predictor variables, namely "root," "CA1," "CA3," and "LGd," to develop a prediction model for our response variable, "feedback." LDA is a prediction method known to be relatively robust, meaning it can handle outlier data points without significantly compromising its performance.

```{r}
install.packages("MASS")
library(MASS)
```

```{r}
# Prepare the training data

training_data <- combined_df
lda_model1 <- lda(feedback ~ root +  `CA3` + `CA1`+`LGd`, data = training_data)

```


Section 5 Prediction performance on the test sets
 -------------------------------------------------------
We import the test data into our project.
```{r}
#obtaining test data
testsession=list()
for(i in 1:2){
  testsession[[i]]=readRDS(paste('~/Downloads/test/test',i,'.rds',sep=''))
}
```

We modify the process_session function from earlier to create a trial summary of test sessions 1 and 2.
```{r}
process_testsession <- function(session_num) {
  n.trial <- length(testsession[[session_num]]$feedback_type)
  n.area <- length(unique(testsession[[session_num]]$brain_area))
  
  trial.summary <- matrix(nrow = n.trial, ncol = n.area + 1 + 2 + 1)
  
  for (i.t in 1:n.trial) {
    trial.summary[i.t,] <- c(average_spike_area(i.t, this_session = testsession[[session_num]]),
                            testsession[[session_num]]$feedback_type[i.t],
                            testsession[[session_num]]$contrast_left[i.t],
                            testsession[[session_num]]$contrast_right[i.t],
                            i.t)
  }
  
  colnames(trial.summary) <- c(names(average_spike_area(i.t, this_session = testsession[[session_num]])),
                               'feedback', 'left contr.', 'right contr.', 'id')
  
  trial.summary <- as_tibble(trial.summary)
  
  return(trial.summary)
}

```

Now we run LDA on both test sessions.
```{r}
testdata1<-process_testsession(1)
testdata2 <- process_testsession(2)

testdata1$CA1<-0
testdata1$LGd<-0
testdata2$CA1<-0


# Step 4: Use the LDA model for prediction
predictionsdata1 <- predict(lda_model1, newdata = testdata1)
predictionsdata2 <- predict(lda_model1, newdata = testdata2)
# Step 5: Extract the predicted feedback values
predictionsdata1
predictionsdata2

```


Section 5 Discussion. 
--------------------------------------------------------
In summary, our prediction model showed limited effectiveness as it consistently predicted a feedback type of "1" in all 100 trials, albeit with varying probabilities. Several flaws in our data analysis contribute to this outcome. Firstly, relying solely on the similarity in mice's response time does not fully account for the similarity in their overall neuron activity or their performance in the experiment. Moreover, selecting brain areas such as "root," "CA1," "CA3," and "LDd" as significant predictors based on their activity in the most sessions may not have been the most optimal choice.

Additionally, our use of the LDA model has its own limitations. LDA struggles with imbalanced classes, where certain topics or in this case, feedback types, are much more prevalent than others. This may result in inaccurate predictions for the minority classes and inappropriate assignment of probabilities.

To improve our predictions, we need to conduct a more in-depth analysis of our data, focusing on better extraction of neural activity. This will allow us to gain a better understanding of the underlying patterns and enable us to make more accurate predictions for different feedback types.


References
---------------------------------------------------------
Steinmetz, N.A., Zatka-Haas, P., Carandini, M. et al. Distributed coding of choice, action and engagement across the mouse brain. Nature 576, 266–273 (2019). https://doi.org/10.1038/s41586-019-1787-x

OpenAI. (2023). ChatGPT  [Large language model]. https://chat.openai.com